---
title: 'Exercise #3'
author: "Qiaomu_Lu(12265424)"
date: "2024-05-27"
output: html_document
subtitle: "Fortgeschrittene Statistische Software für NF - SS 2024"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(readxl)
library(tidyr)
```

# Exercise 1

## 1d)
Strengths: 

1. Very hard to lose files with git.

2. Great for collaboration.

Weaknesses: 

1. Not good for storing data.

2. Man need to use it explicitly, instead in the background.


# Exercise 2

## 2b)
The datatype of variable "anzahl" in these data sets are not numeric, but character.

I used function "transform()". It changed the datatype of "anzahl" successfully, however there were "4 oder weniger" as values in the raw dataframes, which turned into NA after I using "transform()".
```{r 2b}
vornamen_2022 <- read.csv("data/open_data_portal_2022.csv")
vornamen_2023 <- read.csv("data/vornamen-muenchen-2023.csv")

vornamen_2022_2b <- setNames(vornamen_2022, tolower(colnames(vornamen_2022)))
vornamen_2023_2b <- setNames(vornamen_2023, tolower(colnames(vornamen_2023)))

typeof(vornamen_2022_2b$anzahl)
typeof(vornamen_2023_2b$anzahl)

vornamen_2022_2b <- transform(vornamen_2022_2b, anzahl = as.numeric(anzahl))
vornamen_2023_2b <- transform(vornamen_2023_2b, anzahl = as.numeric(anzahl))
```

## 2c)
Not counting the babies with the first names, which have less than 5 owners, the babies born in Munich in 2022 was 9899 and in 2023 was 9277. Year 2022 had the bigger baby-boom.
```{r 2c}
sum(vornamen_2022_2b$anzahl, na.rm = TRUE)
sum(vornamen_2023_2b$anzahl, na.rm = TRUE)
```

## 2d)
```{r 2d}
vornamen_2022_2d <- vornamen_2022_2b %>% mutate(year = 2022)
vornamen_2023_2d <- vornamen_2023_2b %>% mutate(year = 2023)
```
