---
title: 'Exercise #3'
author: "Qiaomu_Lu(12265424)"
date: "2024-05-27"
output: html_document
subtitle: "Fortgeschrittene Statistische Software für NF - SS 2024"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(readxl)
library(tidyr)
```

# Exercise 1

## 1d)
Strengths: 

1. Very hard to lose files with git.

2. Great for collaboration.

Weaknesses: 

1. Not good for storing data.

2. Man need to use it explicitly, instead in the background.


# Exercise 3

## 3b)
The datatype of variable "anzahl" in these data sets are not numeric, but character.

I used function "transform()". It changed the datatype of "anzahl" successfully, however there were "4 oder weniger" as values in the raw dataframes, which turned into NA after I using "transform()".
```{r 3b}
vornamen_2022 <- read.csv("data/open_data_portal_2022.csv")
vornamen_2023 <- read.csv("data/vornamen-muenchen-2023.csv")

vornamen_2022_3b <- setNames(vornamen_2022, tolower(colnames(vornamen_2022)))
vornamen_2023_3b <- setNames(vornamen_2023, tolower(colnames(vornamen_2023)))

typeof(vornamen_2022_3b$anzahl)
typeof(vornamen_2023_3b$anzahl)

vornamen_2022_3b <- transform(vornamen_2022_3b, anzahl = as.numeric(anzahl))
vornamen_2023_3b <- transform(vornamen_2023_3b, anzahl = as.numeric(anzahl))
```

## 3c)
Not counting the babies with the first names, which have less than 5 owners, the babies born in Munich in 2022 was 9899 and in 2023 was 9277. Year 2022 had the bigger baby-boom.
```{r 3c}
sum(vornamen_2022_3b$anzahl, na.rm = TRUE)
sum(vornamen_2023_3b$anzahl, na.rm = TRUE)
```

## 3d)
```{r 3d}
vornamen_2022_3d <- vornamen_2022_3b %>% mutate(year = 2022)
vornamen_2023_3d <- vornamen_2023_3b %>% mutate(year = 2023)
```

## 3e)
```{r 3e}
vornamen_combined_3e <- bind_rows(vornamen_2022_3d, vornamen_2023_3d)
```

## 3f)
```{r 3f}
vornamen_combined_3f <- vornamen_combined_3e %>%
  select(vorname, anzahl) %>%
  na.omit()

vornamen_combined_3f <- 
  aggregate(vornamen_combined_3f$anzahl,
            list(vornamen_combined_3f$vorname),
            FUN = sum) %>%
  rename(anzahl = x, vorname = Group.1) %>%
  arrange(desc(anzahl)) %>%
  head(n = 10)

ggplot(vornamen_combined_3f) + 
  aes(
    x = vorname,
    y = anzahl
  ) + 
  geom_col() + 
  labs(
    x = "First Names",
    y = "Owner Amount",
    title = "Most Popular Names New Born Babies",
    subtitle = "in Munich in year 2022 and 2023",
    caption = "https://opendata.muenchen.de/dataset/vornamen-von-neugeborenen"
  ) 
```

# Exercise 4

## 4a)
```{r 4a}

```